Busch, Khakhalin. Intrinsic temporal tuning

### 2019-04-12 reviews and responses.md

Reviews and Authors' Responses for (Busch Khakhalin 2019)
======================

Here you can see peer-reviews for our paper, given in reverse chronological order, and our point-by-point responses to these reviews. Reviews are split into paragraphs, with  responses and comments given after each paragraph.

--------------------------

# Reviews from J Neurophysiol, 2019 Mar 04 (revise and resubmit)

We address the concerns of Reviewer 3 first, as they were more critical. Then we respond to the suggestions of Reviewer 2.

## Reviewer 3

> Busch and Khakhalin use the Xenopus tadpole tectal model to address the question of
how neurons modify their intrinsic properties when an animal experiences different
types of sensory input. Animals that underwent different forms of sensory experience
had tectal neurons that decreased their overall excitability. This is consistent with the
idea of homeostatic regulation of intrinsic properties. Surprisingly, when the sensory
experience involved short pulses of light, neurons because more responsive to short
inputs even though there was an overall decrease in spiking. This adds a layer of
complexity to the idea of homeostatic control of a firing rate set point because it shows
neurons can independently regulate total spiking in the opposite direction from their
responses to synaptic inputs of different durations. This is a really interesting idea. The
data are sound and well-analyzed (beautiful figures, open source data, etc.). However,
from top to bottom, this manuscript was incredibly difficult to read. Due to organizational
issues, lack of a strong rationale, and inconsistent/confusing wording, I’m not entirely
sure I understand the main message the authors are trying to convey. My summary is
largely based on what I was able to pick out of the figures. I strongly suggest the
authors perform a massive rewrite and really emphasize the main points.

### Major Comments

> Abstract:

> It’s hard to follow what was actually done and found in the paper based on the abstract.
The abstract starts off with a statement about homeostatic regulation through changes
in intrinsic properties and then gives a detailed account of what was found without any
context. It would be easier to assimilate the information if the abstract follows a more
standard format: start with the area the paper clearly contributes to, build the rationale
for the study, state the hypothesis (or driving question), describe how this was tested
and what was found, and say why it’s important.

> I feel the same way about the introduction as I do the abstract; as written, it doesn’t give
the reader a great sense of what’s to come. If the setup for the paper is that
“connectivity isn’t everything— intrinsic properties matter,” this is a good start, but it
could be made much clearer. Further, the questions of the study are not presented until
the third paragraph, and there is no rationale for these questions. I suggest the authors
completely revamp the introduction in way that guides the reader from
regulation/plasticity of intrinsic properties (the big picture question) to why there’s a
reason to think neurons in their system can tune their responsiveness to different kinds
of inputs they receive (a specific hypothesis). This is what the authors actually address,
but they really don’t provide much of a rationale for their specific experiments, which
weakens the paper.

> Results and Discussion:

> - The rationale for the use of dynamic clamp and the parameters chosen are not clear.
Is the dynamic clamp current injection protocol mimicking the physiological synaptic
input? This should be stated.

> - I think the experiment in this study is pretty straightforward, but the description of the
results is not. As far as I can tell, tadpoles were exposed to different stimuli (flash,
looming, multisensory, etc.). Then, tectal neurons were stimulated using either 1)
dynamic clamp or 2) more physiologically through optic chiasm. This allowed the
investigators to assess firing when they changed the stimulus intensity and stimulus
duration of the dynamic clamp or the synaptic response to presynaptic stimulation.
They then looked how the different types of sensory experience influenced firing
responses. The rest is data analysis that looks at how the duration, amplitude, total
spiking, and synaptic input is changed in different sensory contexts and sensory
stimuli might interact. I think the text can be made much simpler so the basic design
is easier to grasp. I suggest thinking about what the take home point is for each
figure and craft the results section around those messages.

> - There is also an inconsistent use terminology. For example, “spikiness” and
“excitability” are sometimes used in attempt to describe distinct cell characteristics,
but sometimes it seems like they are being used interchangeably. This makes
interpreting the written results difficult to follow.

> - “Compared to control, neurons from animals exposed to visual stimuli had a flatter
amplitude tuning curve (Fig 1D,E).” What is the reader supposed to be looking at in
the figure? Is this referring to larger conductances for a fixed duration? I think this is
what the authors’ mean, but more intuitive descriptions that matches the figures or
vice versa is needed to make the whole results section easier to digest.

> - Excessive wordiness makes the results difficult to read and interpret. For example,
on pg. 9, 4 paragraphs (411 words) are used to describe two graphs, each showing
a different linear relationship (Fig. 3E-F). Why not simply say, “A positive relationship
between temporal tuning and synaptic duration implies a co-tuning of these
parameters.”

> - In reference to the text at the bottom of page10: Is it possible to include a summary
figure of data from the stepwise generalized linear model in Fig. 4? The purpose of
this part of the study was to try and identify electrophysiological mechanism(s) that
explain the tuning variables. The heart of Fig. 4 should be that they don’t, and figure
that captures this would be helpful.

> - If these data are interpreted as homeostatic (neurons became less excitable
following sensory experience), is there any evidence that tectal neurons have
different firing activities during the different kinds of sensory experience? For
example, does sound engage tectal neurons less than visual stimuli, and might this
explain some of the trends in the data?

## Reviewer 2

> Busch and Khakhalin use dynamic clamp to generate synaptic conductances of different durations and
then measure the number of action potentials the neurons fire in response to the different
conductances. Using this approach it is found that intrinsic excitability of tectal neurons is temporally
tuned – meaning that they fire best in response to certain durations of synaptic input. This finding is
interesting and unique because typically intrinsic excitability is quantified by generating “input-output”
curves which only vary the amplitude of the synaptic drive, not the duration. Furthermore, the authors
find that various visual stimuli lead to an “adaptive” – not homeostatic – type of temporal tuning of
intrinsic properties such that neurons exposed to shorter stimuli became more responsive to shorter
stimuli and less responsive to longer stimuli., and visa versa. In this study, the effects of visual and
auditory conditioning (and combos thereof) on temporal tuning of both synaptic and intrinsic
excitability are determined. Overall, this study makes great use of dynamic clamp. The interpretation of
the results is limited because the ways in which the conditioning stimuli actually activate tectal neurons
is not empirically established. Clarification, simplification, and consistent use of terms would improve
this paper.

### Minor

> Page 5, line 45/46: “As one possible explanation, auditory and mechanosensory inputs may have
different cellular or subcellular 46 targets in the tectum (Bollmann and Engert, 2009).”
This Bollmann and Engert reference does not address mechanosensory and auditory inputs. This paper
shows that the RGC inputs form a topographic map along the proximal-distal axis of individual tectal
neuron dendrites. This reference should be replaced with an appropriate reference.
Also, how can having different subcellular targets could explain the results? This concept needs to be
clarified – an example would be helpful.

> Page 13 line 46: The authors use the term “distributed sensory network” . Is a “distributed” network a
special type of sensory network?

> Page 3, line 26,27,28: “In the tadpole tectum, looming stimuli are known to elicit stronger responses
compared to instantaneous inversions, yet the suppression yielded by looming stimuli was weaker”.
The logic of this sentence is not clear. Why exactly would the authors not expect that the looming
stimuli that is known to elicit stronger (synaptic?) responses would also cause less suppression (of action
potentials?) than does flashes?

### Major

> Page 5, line 2,3,4 : But do the authors actually know how/if their conditioning stimuli is altering the
pattern/strength of synaptic input? If so, this data should be shown. If not, it should be made clear that
this is an assumption/ theoretical prediction.

> Page 5, line 5: “As changes in intrinsic properties seemed homeostatic (increased activation led to
reduced spiking), by the same logic, one could expect shorter stimuli (flashes) to selectively suppress
responses (action potential firing or synaptic responses or both?) to shorter synaptic inputs”.
What intrinsic properties were measured? It appears that only number of spikes was counted. The
authors report that long-term increase in activation (by visual stimuli) decreased spiking – but was that
due to a decrease in intrinsic excitability or because the stimuli decreased synaptic strengths – which in
turn led to the observed decrease in number of spikes fired? This is critical to define.
Second, do the authors mean to say that shorter stimuli would actually (somehow) suppress responses?
How would that work?

> Page 5 line 15: Does the word “preferred” (in quotes) mean that the cells fired more action potentials?
Maybe refrain from personification.

> Bottom of page 5, “Effects of acoustic and multisensory stimulation:

> - Is the Auditory stim conditioning referred to as “click sounds” the same as the “startle-inducing
sounds” that is mentioned in the very next sentence? If these are indeed the same stimulus it should
be referred to by the same name, consistently. If they are not the same stimuli, the differences need to
be explained.

> - Tadpoles are exposed to 4 hours of click sounds and then intrinsic tuning was measured. No difference
in spiking was observed. This was interpreted to mean that acoustic stimuli did “not strongly activate
tectal circuits during conditioning”. How can the authors know this? Instead, why not determine this
directly by recording click-evoked responses from tectal neurons? Or, if tectal cell responses to auditory
stimuli have been described in previous work, this should be included here.

> Page 6 line 24: Remove the phrase “are not easily interpretable”. Instead, please interpret your data
clearly.

> Page 9: The authors report that the synaptic data show that “prolonged sensory activation with short,
frequent stimuli reshaped synaptic transmission in the tectum, making it faster through selective
potentiation of visual inputs from the eye”.
How do the authors know the effect is selective for RGC inputs? It appears that they only measured
RGC-evoked responses. Auditory/mechanosensory -evoked responses were not reported.

> Page 9 line 9: “cells exposed to stronger stimuli preferred shorter synaptic inputs in dynamic clamp…”
Here, (where “preferred” is not in quotes) does “preferred” mean to fire more action potentials?

> Page 10 (last paragraph): Were action potential thresholds measured? Were there any differences in
this parameter across groups?

> Page 10 line 8: The “correction for position” is difficult to understand here and in Methods. Why was a
linear regression used – and how is it determined to generate an accurate “correction”? How do the
data look without this correction?

> Page 13, line 7: What does “intrinsic spikiness” mean? Is this another term for intrinsic excitability, or is
this a different parameter? In fact, throughout the manuscript, there are many terms including “intrinsic
excitability, spikiness, number of spikes, and intrinsic spikiness that probably mean the same thing – or
maybe not. If these terms all mean the same thing, then one term should be chosen and used
throughout. If they all refer to different entities, then each one should be clearly defined.

> Page 15 line 34: The average membrane resistance (330 MOhm) seems a bit low for these small immature
tectal neurons. Were the neurons healthy? What was the average resting membrane potential? Were
there any set criteria for Rm, Vm, or access resistance?

> Figure 1 D and E: The average number of spikes fired as a function of conductance duration and all at 3
different peak conductances. Are there any trends at the single cell level? For example, if a given
control neuron fires relatively few spikes in response to 500 ms duration, does it also tend to fire
relatively fewer spikes with 1000ms duration? Or maybe if a given neuron fires a relatively high number
of spikes with 500ms then it will typically fire less at 1000ms duration? Although the individual
responses are shown in 1D, it is impossible to follow the number of spikes fired by any individual neuron
in response to the different conductance durations.

> Figure 4 D, E and F: Is “spikiness” synonymous with “N Spikes”? If these terms do not mean the same
thing, they should be defined. If they do mean the same thing, then one term should be chosen and
used consistently throughout.

--------------------------

### 2019-04-12 reviews and responses.md

Here you can see peer-reviews for our paper, given in reverse chronological order, and our point-by-point responses to these reviews. Reviews are split into paragraphs, with  responses and comments given after each paragraph.

--------------------------

# Reviews from J Neurophysiol, 2019 Mar 04 (revise and resubmit)

We address the concerns of Reviewer 3 first, as they were more critical overall. Then we respond to the suggestions of Reviewer 2.

@@

### Major Comments

> Abstract:

> It’s hard to follow what was actually done and found in the paper based on the abstract.
The abstract starts off with a statement about homeostatic regulation through changes
in intrinsic properties and then gives a detailed account of what was found without any
context. It would be easier to assimilate the information if the abstract follows a more
standard format: start with the area the paper clearly contributes to, build the rationale
for the study, state the hypothesis (or driving question), describe how this was tested
and what was found, and say why it’s important.

We rewrote the abstract, stressing the big question to which the paper contributes (principles of tuning and learning in biological neural networks), and the main message of the paper. We also made the account of our findings a bit less detailed.

@@

> Introduction:

> I feel the same way about the introduction as I do the abstract; as written, it doesn’t give
the reader a great sense of what’s to come. If the setup for the paper is that
“connectivity isn’t everything— intrinsic properties matter,” this is a good start, but it
could be made much clearer. Further, the questions of the study are not presented until
the third paragraph, and there is no rationale for these questions. I suggest the authors
completely revamp the introduction in way that guides the reader from
regulation/plasticity of intrinsic properties (the big picture question) to why there’s a
reason to think neurons in their system can tune their responsiveness to different kinds
of inputs they receive (a specific hypothesis). This is what the authors actually address,
but they really don’t provide much of a rationale for their specific experiments, which
weakens the paper.

We tried to make the introduction more clear, and better organized, from the big problem, to specific questions. We moved the presentation of the questions for the study to the very beginning of the second paragraph, and provide a rationale for these questions in the first paragraph.

### 2019-04-12 main.tex
text: abstract and intro, draft revision

%\rhead{Busch SE, Khakhalin AS. Temporal tuning in the tectum. Page \thepage}
%\cfoot{} % To kill footer page numbers

@@

\rfoot{Busch SE, Khakhalin AS. Temporal tuning in the tectum. Page \thepage}
\renewcommand{\headrulewidth}{0pt} % To remove top line
\renewcommand{\footrulewidth}{1pt} % To add bottom line
\fancyhead{} % Removes all headers
\cfoot{} % Kills middle footer

@@

%\linenumbers % Comment this to suppress line numbers

@@

\section*{Abstract}
% 150 words (149 as or Aug 07)

Homeostatic intrinsic plasticity is often described as an adjustment of neuronal excitability to maintain stable spiking output. Here we report that intrinsic plasticity in the tectum of Xenopus tadpoles also supports temporal tuning, wherein neurons independently adjust spiking responses to fast and slow patterns of synaptic activation. Using the dynamic clamp technique, and five different types of visual, acoustic, and multisensory conditioning, we show that in tadpoles exposed to light flashes, tectal neurons became selective for fast synaptic inputs, while neurons exposed to looming and multisensory stimuli remained responsive to longer inputs. We also report a homeostatic co-tuning between synaptic and intrinsic temporal properties in tectal cells, as neurons that naturally received fast synaptic inputs tended to be most responsive to long-lasting synaptic conductances, and the other way around. These results expand our understanding of plasticity in the brain, and inform future work on the mechanisms of sensorimotor transformation.

@@

\section*{Significance statement}
% 119 words (limit 120)
%TC:endignore
With the recent explosion of work in neural connectivity reconstruction and biologically inspired deep learning, most researchers concentrate on the topology of connections between neurons, rather than on differences in neuronal tuning. Here we show that in a sensory network in Xenopus tadpoles, different neurons are tuned, and respond stronger, to either short or long synaptic inputs. This tuning tended to be opposite to the actual dynamics of synaptic inputs each cell received, such that neurons that normally receive shorter inputs generated stronger spiking in response to longer testing currents, and the other way around. This observation shows that even in networks that don't generate oscillations, neurons reshape their temporal selectivity, to optimize their impact on distributed calculations. 
%TC:ignore 
\bigskip

@@

It is often assumed, in fields as diverse as connectomics and machine learning, that the main difference between functional and dysfunctional neural networks lies in their connectivity \citep{takemura2014,hildebrand2017,bassett2017network,reimann2017}. Biological neurons, however, are tuned in ways that go well beyond adjusting one “strength” value per synapse: cells within the same network often demonstrate variability of activation thresholds \citep{kole2012}, production of bursts \citep{popovic2011}, inactivation by strong inputs \citep{bianchi2012}, and more. This diversity of tuning relies on coordinated changes of many parameters across a complex, multivariate landscape \citep{oleary2013}, as neuronal phenotypes are shaped by sensory experiences, and adjusted by modulatory inputs \citep{evans2015}. The dysregulation of intrinsic plasticity affects network dynamics \citep{tien2018}, and can lead to a loss of function \citep{marcelin2009}. And yet, with the obvious exception of oscillatory networks \citep{marder2011,picton2018control}, for many brain areas it is still unclear whether variation of intrinsic phenotypes serves as a defining aspect of network topology and architecture, or whether it is just a consequence of transfer function normalization \citep{titley2017}.

The optic tectum of the \textit{Xenopus} tadpole is an ideal model for exploring these questions: it is a highly malleable distributed network of about $10^4$ neurons \citep{pratt2013}, involved in stimulus discrimination and sensorimotor transformations \citep{dong2009,khakhalin2014}. In development, tectal neurons acquire diverse intrinsic and synaptic phenotypes that are also shaped by sensory experiences \citep{xu2011,ciarleglio2015}. Circuits in the tectum can learn and reproduce the temporal dynamics of inputs to which they were exposed \citep{pratt2008}: a property that could in principle be achieved through synaptic changes alone \citep{lukovsevivcius2009}, but which is more likely to involve intrinsic temporal tuning \citep{narayanan2008,beatty2014}. Finally, tectal neurons exhibit strong Na channel inactivation, which seems to play a role in collision detection \citep{jang2016}, and is one of the targets for intrinsic plasticity \citep{bianchi2012}.

In this study, we asked two specific questions about the properties of intrinsic plasticity in tectal networks. First, we asked whether intrinsic plasticity is limited to changes in excitability, or whether it is more nuanced and can differentially adjust neuronal responsiveness to inputs with different dynamics. Second, we checked whether changes in intrinsic properties in the tectum are a homeostatic response to each cell's history of synaptic activation, or if they are independent of synaptic properties. In our previous large-scale census of tectal cells \citep{ciarleglio2015}, we observed no interaction between intrinsic and synaptic phenotypes, and despite an extensive search, we did not detect signs of temporal tuning (ibid,  figures 2, 4). However, we propose that the standard current-clamp protocols used in previous studies \citep{pratt2007,hamodi2014} were not adequate to detect important changes in the function of voltage-gated channels (see Discussion).

Here we show that the intrinsic plasticity of tectal neurons goes beyond changes in average spikiness and supports temporal selectivity that can be reshaped by sensory experience. Furthermore, we show that the tuning of intrinsic properties is coordinated with the duration of synaptic inputs received by each cell. These results rely on two methodological innovations. First, instead of using current injections, we employed the dynamic clamp technique, which allowed a more realistic simulation of synaptic conductances \citep{prinz2004}. Unlike more common voltage and current clamp techniques, in dynamic clamp the electric current injected into the cell is dynamically adjusted, based on a predefined formula that depends on cell membrane potential and time. Second, instead of relying on one type of sensory stimulation, we used five different stimulation protocols and compared their effects on intrinsic tuning. The use of different sensory modalities also gave us insight into an unrelated, but equally intriguing question of multisensory integration in the brain \citep{deeg2009,felch2016,truszkowski2017}, as for the first time we were able to look at tectal network retuning in response to multisensory stimuli in freely behaving tadpoles.

>>>>

\rhead{Busch SE, Khakhalin AS. Temporal tuning in the tectum. Page \thepage}
\cfoot{} % To kill footer page numbers

@@

%\rfoot{Busch SE, Khakhalin AS. Temporal tuning in the tectum. Page \thepage}
%\renewcommand{\headrulewidth}{0pt} % To remove top line
%\renewcommand{\footrulewidth}{1pt} % To add bottom line
%\fancyhead{} % Removes all headers
%\cfoot{} % Kills middle footer

@@

\linenumbers % Comment this to suppress line numbers

@@

\section*{Abstract}
% J Neurophysiol: up to 250 words
% Currently: 184

For a biological neural network to be functional, its neurons need to be connected to each other with synapses of appropriate strength, but also each neuron needs to appropriately respond to its synaptic inputs. This second aspect of network tuning is maintained by intrinsic plasticity; yet it is often considered secondary to changes in connectivity, and mostly limited to adjustments of overall excitability of each neuron. Here we argue that individual neurons are also tuned to inputs of different temporal dynamics, and that they can routinely adjust this tuning to match the statistics of their synaptic activation. Using the dynamic clamp technique, we show that in the tectum of Xenopus tadpoles, neurons become selective for faster inputs in animals that were exposed to fast visual stimulation, but remain responsive to longer inputs in animals exposed to looming or multisensory stimulation. We also report a homeostatic co-tuning between synaptic and intrinsic temporal properties of individual tectal cells. These results expand our understanding of plasticity in the brain, and suggest that there may exist a whole extra dimension of network tuning that was so far overlooked.

%Old version: Homeostatic intrinsic plasticity is often described as an adjustment of neuronal excitability to maintain stable spiking output. Here we report that intrinsic plasticity in the tectum of Xenopus tadpoles also supports temporal tuning, wherein neurons independently adjust spiking responses to fast and slow patterns of synaptic activation. Using the dynamic clamp technique, and five different types of visual, acoustic, and multisensory conditioning, we show that in tadpoles exposed to light flashes, tectal neurons became selective for fast synaptic inputs, while neurons exposed to looming and multisensory stimuli remained responsive to longer inputs. We also report a homeostatic co-tuning between synaptic and intrinsic temporal properties in tectal cells, as neurons that naturally received fast synaptic inputs tended to be most responsive to long-lasting synaptic conductances, and the other way around. These results expand our understanding of plasticity in the brain, and inform future work on the mechanisms of sensorimotor transformation.

@@

%\section*{Significance statement}
%%%TC:endignore
%With the recent explosion of work in neural connectivity reconstruction and biologically inspired deep learning, most researchers concentrate on the topology of connections between neurons, rather than on differences in neuronal tuning. Here we show that in a sensory network in Xenopus tadpoles, different neurons are tuned, and respond stronger, to either short or long synaptic inputs. This tuning tended to be opposite to the actual dynamics of synaptic inputs each cell received, such that neurons that normally receive shorter inputs generated stronger spiking in response to longer testing currents, and the other way around. This observation shows that even in networks that don't generate oscillations, neurons reshape their temporal selectivity, to optimize their impact on distributed calculations. 
%%%TC:ignore 
\bigskip

@@

It is often assumed, in fields as diverse as connectomics and machine learning, that the main difference between functional and dysfunctional neural networks lies in their connectivity \citep{takemura2014,hildebrand2017,bassett2017network,reimann2017}. However, biological neurons also demonstrate complex and multifaceted intrinsic tuning  \citep{oleary2013,evans2015}, with cells within a single network having different activation thresholds \citep{kole2012}, bursting behaviors \citep{popovic2011}, and inactivation profiles \citep{bianchi2012}. Dysregulation of intrinsic plasticity affects the dynamics of networks  \citep{tien2018}, and can lead to a loss of function \citep{marcelin2009}. And yet, with the possible exception of oscillatory networks \citep{marder2011,picton2018control}, the logic of intrinsic plasticity, and its contribution to network tuning, remain unclear. We know that neurons adjust their spikiness to match the levels of synaptic activation they experience \citep{aizenman2003,titley2017}, but biophysically, they often also have the means to become tuned to different temporal patterns of activation \citep{jarvis2018morphology,ohtsuki2018bursting}. Do they rely on this type of tuning in practice?

In this paper, we investigate whether exposure to sensory stimuli of different temporal dynamics would change intrinsic temporal tuning of sensory neurons in the optic tectum of \textit{Xenopus} tadpoles. Tadpole tectum is an ideal model for exploring this question: it is a highly malleable distributed network of about 10\textsuperscript{4} neurons \citep{pratt2013}, involved in stimulus discrimination and sensorimotor transformations \citep{dong2009,khakhalin2014}. In development, tectal neurons acquire diverse phenotypes, that are then shaped by sensory experiences \citep{xu2011,ciarleglio2015}. Circuits in the tectum can learn and reproduce temporal patterns to which they were exposed \citep{pratt2008}: a property that could in principle be achieved through synaptic changes alone \citep{lukovsevivcius2009}, but which would be easier to achieve through intrinsic temporal tuning \citep{narayanan2008,beatty2014}. Finally, tectal neurons exhibit strong Na channel inactivation, which seems to play a role in collision detection \citep{jang2016}, and is a known target for intrinsic plasticity mechanisms \citep{bianchi2012}.

Specifically, we ask two questions about the properties of intrinsic plasticity in tectal networks. First, we check whether intrinsic plasticity is limited to changes in overall excitability, or whether it differentially retunes neuronal responses to faster and slower inputs. Second, we ask whether intrinsic tuning of tectal cells is coordinated with  the typical length of synaptic currents they receive, or whether two types of tuning are independent. In our previously published large-scale census of tectal cells \citep{ciarleglio2015}, we observed no interaction between intrinsic and synaptic phenotypes, and observed no signs of temporal tuning (ibid,  figures 2, 4). We argue however, that the current clamp protocol used in previous studies was not adequate for the task (see Discussion for a rationale).

Instead, here we rely on two methodological innovations. First, we use the dynamic clamp technique, that allows a more realistic simulation of synaptic conductances \citep{prinz2004}. Unlike more common voltage and current clamp techniques, in dynamic clamp the electric current injected into the cell is dynamically adjusted, based on a predefined formula that depends on cell membrane potential and time. Second, instead of relying on one type of sensory stimulation, we used five different stimulation protocols and compared their effects on intrinsic tuning. We show that the intrinsic plasticity of tectal neurons goes beyond changes in average spikiness, and supports temporal selectivity, that is shaped by sensory experience, and is coordinated with the typical duration of synaptic inputs received by each cell. Moreover, the use of different sensory modalities for stimulation gave us an insight into an unrelated, but intriguing question of multisensory integration in the brain \citep{deeg2009,felch2016,truszkowski2017}, as for the first time we were able to look at tectal retuning in response to multisensory experience in freely behaving tadpoles.
